Tracing the Stellar Halo of Massive Galaxies to 100 kpc at $0.3<z<0.5$ using the Hyper Suprime-Cam

### 2017-06-01 draft/paper1_jenny.tex
Edit Discussion 2

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_ell_color.pdf}
      \caption{
          Radial variations in ellipticity and optical colors for massive galaxies. 
          The format of this figure is similar to Fig~\ref{fig:avg_prof}. 
          \textbf{Left panel} shows the ellipticity profiles, 
          \textbf{Upper-right panel} shows the $g-r$ color profiles, and 
          \textbf{Lower-right panel} is for $g-i$ color profiles. 
          We compare our results with those from \citet{Tal2011} based on stacking 
          large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
          (solid red line on left panel). 
          We also compare with the results from a stacking analysis of nearby massive 
          galaxies with high concentration index ($C>2.6$) in 
          \citet[][blue dash lines on the left and upper-right panels]{DSouza2014}. 
          Finally, we also compare with the average $g-r$ and $g-i$ color profiles 
          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
          lines on both right panels]{LaBarbera2010}.
          }
      \label{fig:ell_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_insitu_accretion}
      \caption{
          \textbf{Left:}
          Comparison of the median \mden{} profiles of massive galaxies in the 
          two lower \mtot{} bins from Fig~\ref{fig:avg_prof} with other observations 
          and simulations, focusing on the inner region. 
          The format is similar with the right panel of Fig~\ref{fig:avg_prof}.
          We include: 
          1) the median \mden{} profile of inner component from structure 
          decomposition of massive elliptical galaxies at $z{\sim} 0$ from 
          \citet[][Cyan, solid]{Huang2013a}; 
          2) the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
          from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
          3) the median \mden{} profile of the ``in-situ'' stellar components in 
          simulated massive halos from \citet[][Purple, dot-dashed]{Cooper2013};
          4) the \mden{} profile of the very massive cD galaxy at $z{\sim} 1.1$ 
          discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
          Ultra-Deep Field.
          \textbf{Right:}
          Relation between \mtot{} and the fraction of \mstar{} within 10 to 100 kpc, 
          which is used here as proxy of the fraction of accreted stars. 
          The typical uncertainties of \mtot{} and the mass fraction are shown in 
          upper-left corner. 
          This relation is compared with the relation between \mstar{} and the fraction
          of accreted stars derived from the Illustris simulation at $z=0$ 
          (Fig 4 in \citealt{RodriguezGomez2016}; grey solid and dashed lines). 
          }
      \label{fig:discussion_1}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
\subsection{Aperture Masses as Proxies of In-Situ and Accreted Stars}
    \label{ssec:insitu}

    Recent hydrodynamic simulations of galaxy formation often separate the stars in 
    galaxy into the \textit{in-situ} and accreted components. 
    In simulation, the \textit{in-situ} component is often defined as the stars formed 
    in the halo of the ``main progenitor''.  
    The spatial distribution, kinematic, and stellar population properties of both 
    components become important theoretical predictions to be examined. 
    Among them, the fraction of the accreted component and its relation with stellar 
    mass is the most fundamental one. 
    However, on the observational side, separation of these two physical components 
    is extremely difficult. 
    So far, we have

@@

    We now investigate to what degree our assumption that the inner 10 kpc \mstar{}
    corresponds to an in-situ mass.    
    Fig \ref{fig:discussion_1} compares the median \mden{} profiles of the 
    galaxies in two \mtot{} bins 
    ($11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with 
    (1) the median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
    \citealt{Patel2013} since they are considered as the progenitors of 
    ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$.    
    (2) the inner components of $z{\sim} 0$ ellipticals from 2-D decomposition 
    (\citealt{Huang2013a}).
    As proxy of the in-situ components, \citet{Huang2013b} showed they are 
    structurally similar to the compact ``red nuggets'' at high-$z$. 
    (3) the ``in-situ'' components of simulated central galaxies in massive halos 
    from \citet{Cooper2013} (the inner ${\sim} 5$ kpc is quite uncertain due to the 
    resolution).  
    The comparison confirms that \minn{} should be reasonable proxy of the 
    ``in-situ'' mass\footnote{We convert these \mden{} profiles to the same 
    Chabrier IMF; but there are still differences in median \mstar{} and 
    details in the \m2l{} estimates}.  
    More importantly, it shows that the \mden{} profile at 
    $\mathrm{R} > 15$-20 kpc is likely dominated by stars that are not related 
    to the ``in-situ'' processes.

>>>>

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_ell_color.pdf}
      \caption{
          Radial variations in ellipticity and optical colors for massive galaxies. 
          The format of this figure is similar to Fig~\ref{fig:avg_prof}. 
          \textbf{Left panel} shows the ellipticity profiles, 
          \textbf{Upper-right panel} shows the $g-r$ color profiles, and 
          \textbf{Lower-right panel} is for $g-i$ color profiles. 
          We compare our results with those from (1) \citet{Tal2011} based on stacking 
          large samples of luminous red galaxies in SDSS at $z{\sim} 0.4$ 
          (solid red line on left panel), 
          (2) the results from a stacking analysis of nearby massive 
          galaxies with high concentration index ($C>2.6$) in 
          \citet[][blue dash lines on the left and upper-right panels]{DSouza2014}, 
          (3) and the average $g-r$ and $g-i$ color profiles 
          from a large sample of nearby elliptical galaxies in \citet[][blue, solid 
          lines on both right panels]{LaBarbera2010}.
          For color profiles, we also compare with deep observations of a few nearby 
          massive ETGs: the $g-r$ color profiles of NGC 4472 (\citealt{Mihos2013}) 
          and NGC 4365 (\citealt{Mihos2017}), and the $g-i$ profile of NGC 1399 
          (\citealt{Iodice2016})
          }
      \label{fig:ell_color}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
  \begin{figure*}
      \centering 
      \includegraphics[width=\textwidth]{fig/redbcg_insitu_accretion}
      \caption{
          \textbf{Left:}
          Relation between \mtot{} and the fraction of \mstar{} within 10 to 100 kpc, 
          which is used here as proxy of the fraction of accreted stars. 
          The typical uncertainties of \mtot{} and the mass fraction are shown in 
          upper-left corner. 
          This relation is compared with the relation between \mstar{} and the fraction
          of accreted stars derived from the Illustris simulation at $z=0$ 
          (Fig 4 in \citealt{RodriguezGomez2016}; grey solid and dashed lines). 
          \textbf{Right:}
          Comparison of the median \mden{} profiles of massive galaxies in the 
          two lower \mtot{} bins from Fig~\ref{fig:avg_prof} with other observations 
          and simulations, focusing on the inner region. 
          The format is similar with the right panel of Fig~\ref{fig:avg_prof}.
          We include: 
          1) the median \mden{} profile of inner component from structure 
          decomposition of massive elliptical galaxies at $z{\sim} 0$ from 
          \citet[][Cyan, solid]{Huang2013a}; 
          2) the median \mden{} profile of massive galaxies at $1.0 < z < 1.5$ 
          from \textit{HST} observations in \citet[][Red, dashed]{Patel2013}; 
          3) the median \mden{} profile of the ``in-situ'' stellar components in 
          simulated massive halos from \citet[][Purple, dot-dashed]{Cooper2013};
          4) the \mden{} profile of the very massive cD galaxy at $z{\sim} 1.1$ 
          discovered by \citet[][Yellow, dashed]{Liu2013} in the Hubble 
          Ultra-Deep Field.
          }
      \label{fig:discussion_1}
  \end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %% 
\subsection{Aperture Masses as Proxies of the \textit{In-situ} and Accreted Stars}
    \label{ssec:insitu}

    Recent hydrodynamic simulations of galaxy formation often separate the stars in 
    galaxy into the \textit{in-situ} and accreted components. 
    In simulation, the \textit{in-situ} component is often defined as the stars formed 
    in the halo of the ``main progenitor''.  
    The spatial distribution, kinematic, and stellar population properties of both 
    components become important theoretical predictions to be examined. 
    Among them, the fraction of the accreted component and its relation with stellar 
    mass is the most fundamental one. 
    However, on the observational side, separation of these two physical components 
    is extremely difficult. 
    Recently, deep surveys of nearby disk galaxies start to provide constraints of 
    their accreted fraction using the distinctive halo components. 
    For more massive ETGs, efforts so far all depend on multi-component model fitting
    and image stacking analysis (e.g. \citealt{Huang2013a, dSouza2014, Spavone2017}).
    In this work, we propose that \mstar{} within different physical apertures could 
    be explored as potential proxies of masses in \textit{in-situ} and accreted 
    components.  
    Given the behaviours of the \mden{} profiles shown in Fig \ref{fig:avg_prof}, 
    we propose to use mass within 10 kpc (\minn{}) and 100 kpc (\mtot{}) as proxies 
    of the \textit{in-situ} and total \mstar{}.

    On the left panel of Fig \ref{fig:discussion_1}, we plot the relation between 
    \mtot{} and the fraction of mass between 10 and 100 kpc (as proxy of the mass of 
    the accreted component), and compare with the relation between \mstar{} and 
    accreted fraction derived from the Illustris simulation 
    (\citealt{RodriguezGomez2016}). 
    It is intriguing to see that, our proxy of accreted mass not only strongly 
    correlates with \mtot{}, the relation is surprisingly consistent with the 
    prediction from \citet{RodriguezGomez2016}. 
    Given the different definition of total stellar mass,

@@

    To see whether \minn{} can reasonably represent the \textit{in-situ} mass, we 
    compare the average \mden{} profiles of HSC massive galaxies in two \mtot{} 
    bins (Left panel of Fig \ref{fig:discussion_1}, 
    $11.4\leq$\logmtot{}$<11.6$ and $11.6\leq$\logmtot{}$<11.8$) with:

        \item The median \mden{} profiles of massive ETGs at $1.0 < z < 1.5$ in
            \citealt{Patel2013} since they are considered as the progenitors of 
            ${\sim} 10^{11.5} M_{\odot}$ ETGs at $z=0$ and their inner region 
            should be dominated by \textit{in-situ} stars.

        \item The inner components of $z{\sim} 0$ ellipticals from 2-D 
            decomposition (\citealt{Huang2013a}).
            As proxy of the \textit{in-situ} component, \citet{Huang2013b} showed 
            that they are structurally similar to the compact ``red nuggets'' at 
            high-$z$.

        \item The \textit{in-situ} components of simulated central galaxies in 
            massive halos from \citet{Cooper2013} (the inner ${\sim} 5$ kpc is 
            quite uncertain due to the resolution).  
            These \mden{} profiles are generated using the particle tagging 
            method (see \citealt{Cooper2010})

    The comparison confirms that \minn{} should be reasonable proxy of the 
    ``in-situ'' mass\footnote{We convert these \mden{} profiles to the same 
    Chabrier IMF; but there are still differences in median \mstar{} and 
    details in the \m2l{} estimates}.  
    More importantly, it shows that the \mden{} profile at 
    $\mathrm{R} > 15$-20 kpc is likely dominated by stars that are not related 
    to the ``in-situ'' processes.
